---
title: "Names and Values"
output: html_document
---

## 2.2 Binding Basics 

### Exercise 2.2.1

Explain the relationship between a, b, c and d in the following code:

```{r, eval = FALSE}
a <- 1:10
b <- a
c <- b
d <- 1:10
```

The first line `r a <- 1:10` creates the vector 
`c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)` and assigns the name `a` to it.

The same vector is the assigned to name `b` and name `c`. Note that `a`, `b`, 
and `c` have the same memory location.

The last line creates a second vector `c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)` 
and assigns the name `d` to it. In this case `d` has a different address than 
`a`, `b`, and `c`.

```{r}
a <- 1:10
b <- a
c <- b
d <- 1:10

lobstr::obj_addr(a) == lobstr::obj_addr(b)
lobstr::obj_addr(a) == lobstr::obj_addr(c)
lobstr::obj_addr(a) == lobstr::obj_addr(d)
```

### Exercise 2.2.2

The following code accesses the `mean` function in multiple ways. Do they all 
point to the same underlying function object? Verify this with 
`lobstr::obj_addr()`.

```{r, eval=FALSE}
mean
base::mean
get("mean")
evalq(mean)
match.fun("mean")
```

All methods of accessing a function point to the same object:

```{r}
#https://stackoverflow.com/questions/30850400/using-identical-in-r-with-multiple-vectors
a <- lobstr::obj_addr(mean)
b <- lobstr::obj_addr(base::mean)
c <- lobstr::obj_addr(get("mean"))
d <- lobstr::obj_addr(evalq(mean))
e <- lobstr::obj_addr(match.fun("mean"))

all(sapply(list(b, c, d, e), FUN = identical, a))
```

### Exercise 2.2.3

By default, base R data import functions, like `read.csv()`, will automatically 
convert non-syntactic names to syntactic ones. Why might this be problematic? 
What option allows you to suppress this behaviour?

By default, `read.csv()` will use the `make.names()` function to create 
syntactic column names.

```{r}
testfile <- tempfile(fileext = ".csv")
cat("_abc", "1", "2", "3", file = testfile, sep = "\n")

read.csv(testfile)
```

You can suppress this behaviour by setting the `check.names` argument to 
`FALSE`.

```{r}
read.csv(testfile, check.names = FALSE)
```

### Exericse 2.2.4

What rules does `make.names()` use to convert non-syntactic names into 
syntactic ones?

From the function documentation, in the `make.names()` function:

* The character "X" is prepended if necessary. 
* All invalid characters are translated to ".". 
* A missing value is translated to "NA". 
* Names which match R keywords have a dot appended to them. 
* Duplicated values are altered by make.unique.

For example: 

```{r}
nonsyntactic <- c("_abc", "with space", "if", "with-space")
make.names(nonsyntactic, unique = TRUE)
```

### Exercise 2.2.5

I slightly simplified the rules that govern syntactic names. Why is `.123e1` not 
a syntactic name? Read `?make.names` for the full details.

From the documentation:

"A syntactically valid name consists of letters, numbers and the dot or 
underline characters and starts with a letter or the **dot not followed by a 
number**."

```{r}
make.names(".123e1")
```

