---
title: "Chapter 3: Vectors"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 3.2 Atomic Vectors

### Exercise 3.2.1 

How do you create raw and complex scalars? (See `?raw` and `?complex`)

Scalars in R are really just vectors of length 1. For `raw()` we specify 
this using the `length` argument, and for `complex()` we use the `length.out` 
argument.

```{r}
raw(length = 1)
complex(length.out = 1)
```

### Exercise 3.2.2

Test your knowledge of the vector coercion rules by predicting the output of 
the following uses of `c()`:

```{r, eval = FALSE}
c(1, FALSE)
c("a", 1)
c(TRUE, 1L)
```

Remember the order of flexibility: logical --> integer --> double --> character.

* `c(1, FALSE)` will be of type double --> `c(1, 0)`
* `c("a", 1)` will be of type character --> `c("a", "1")`
* `c(TRUE, 1L)` will be of type integer --> `c(1, 1)`

```{r}
c(1, FALSE)
c("a", 1)
c(TRUE, 1L)
```

### Exercise 3.2.3

Why is `1 == "1"` true? Why is `-1 < FALSE` true? Why is `"one" < 2` false?

Again, remember the order of flexibility: logical --> integer --> double --> 
character.

* `1 == "1"` is actually testing `"1" == "1"`, which is `TRUE`
* `-1 < FALSE` is coerced to `-1 < 0`, which is `TRUE`
* `"one" < 2` is coerced to `"one" < "2"`, which is `FALSE`

```{r}
1 == "1"
-1 < FALSE
"one" < 2
```

### Exercise 3.2.4

Why is the default missing value, `NA`, a logical vector? What’s special about 
logical vectors? (Hint: think about `c(FALSE, NA_character_)`.)

Think about `c(FALSE, NA_character_)`:

```{r}
typeof(c(FALSE, NA_character_))
```

Note the type coercion that takes place. Since `NA` is a logical vector, it has 
the flexibility to be coereced up to different data types.

```{r}
typeof(c(TRUE, NA))
typeof(c(1L, NA))
typeof(c(1, NA))
typeof(c('one', NA))
```

### Exercise 3.2.5

Precisely what do `is.atomic()`, `is.numeric()`, and `is.vector()` test for?

From the documentation,

* `is.atomic` returns `TRUE` if `x` is of an atomic type (or `NULL`) and 
`FALSE` otherwise.

```{r}
x <- c(1L, 2L, 3L)
is.atomic(x)
is.atomic(list(x))
```

* `is.numeric` is a more general test of an object being interpretable as 
numbers.

```{r}
is.numeric(c("a", "b", "c"))
is.numeric(c(1L, 2L, 3L))
is.numeric(c("1", "2", "3"))
is.numeric(factor(c(1L, 2L, 3L)))
```

* `is.vector` returns `TRUE` if `x` is a vector of the specified `mode` having 
no attributes other than names. It returns `FALSE` otherwise.

Note that if `mode = "any"`, `is.vector` may return `TRUE` for the atomic 
modes, list and expression.

```{r}
x <- c(1L, 2L, 3L)

is.vector(x)
is.vector(x, mode = "character")
is.vector(list(x))
```

